Recpature distances

### 2025-01-23 recaptureanalysis/recaps.Rmd
One more tweak to the figure.

#lookout
lookout = filter(recaps2,  Site == "Lookout Slough", !is.na(Latitude))
los = filter(release, Site == "Lookout Slough") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst5 = GGdist(Water_map = spacetools::Delta, Points = lookout, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = los)

@@

distances = bind_rows(tesst, tesst2, tesst3)
```

@@

```{r}
library(cder)
library(zoo)

@@

turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
summary(turbm)
#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.

>>>>

#lookout
lookout = filter(recaps2,  Site == "Lookout Slough", !is.na(Latitude))
los = data.frame(Latitude = 38.318509, Longitude = -121.6935146) %>%
  distinct()
tesst5 = GGdist(Water_map = spacetools::Delta, Points = lookout, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = los)

@@

distances = bind_rows(tesst, tesst2, tesst3, tesst4, tesst5)
```

@@

```{r}
library(cder)
library(zoo)
library(effects)

@@

turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
summary(turbm)
plot(allEffects(turbm))
#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.
